Reaching is Better When You Get What You Want: Realtime Feedback of Intended Reaching Trajectory Despite an Unstable Environment

### 2015-05-06 Paper2frontiers/frontiers.tex
mild intro updates

\title[Realtime Feedback of Intended Trajectory]{Reaching is Better When You Get What You Want: Realtime Feedback of Intended Reaching Trajectory Despite an Unstable Forces}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
\topic{}% If your article is part of a Research Topic, please indicate here which.

@@

While performance is the best indicator of IF's value, changes in arm stiffness can provide secondary confirmation that subjects are actually getting what they want. Arm stiffness is known to increase during exposure to instability \cite{franklin2003adaptation} and uncertainty \cite{takahashi2001impedance}. We anticipated that these change might also be modulated by presentation of IF. Reduces the effects of environmental instability and presenting the subject with a signal already known to them may make the arm relax and become more compliant. We hypothesized that any elevated arm stiffness from noisy disturbances would decrease when subjects received IF.

@@

%\begin{methods}
\section{Material \& Methods}

>>>>

\title[Realtime Feedback of Intended Trajectory]{Reaching is Better When You Get What You Want: Realtime Feedback of Intended Reaching Trajectory Despite an Unstable Environment}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
\topic{}% If your article is part of a Research Topic, please indicate here which.

@@

While performance is the best indicator of IF's value, changes in arm stiffness can provide supporting evidence that subjects are actually getting what they want. Arm stiffness is known to increase during exposure to instability \cite{franklin2003adaptation} and uncertainty \cite{takahashi2001impedance}. We anticipated that these change might also be modulated by presentation of IF. Reducing the effects of environmental instability and presenting the subject with a signal already known to them should make the arm relax and become more compliant. We hypothesized that any elevated arm stiffness from noisy disturbances would decrease when subjects received IF.

@@

\begin{methods}
\section{Material \& Methods}
